---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# Movie (1.0.0)

<!-- badges: start -->-
![](https://github.com/DSCI-310/dsci-310-group-08-pkg/actions/workflows/test_coverage.yaml/badge.svg)
[![codecov](https://codecov.io/gh/DSCI-310/dsci-310-group-08-pkg/branch/main/graph/badge.svg?token=1zVFP2D7XT)](https://codecov.io/gh/DSCI-310/dsci-310-group-08-pkg)
<!-- badges: end -->

The goal of Movie is to provide the user with common useful functions that are useful for reproducing the Movie Budget Analysis. This package is built on many other packages such as ggplot2, GGally and tidyverse. There are other packages such as ggplot2 that can genereate plots similar to the ones that can be generated using this package. Utils can be used to downlaod datasets from the internet but this package gives you all the useful function for the particular type of project mentioned above.

### Functions Included:
- `read_dataset()`
- `EDA()`
- `correlation_plot()`
- `plot_scatter_graph()`

## Installation

You can install the development version of Movie from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("DSCI-310/dsci-310-group-08-pkg")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(Movie)
## basic example code for downloading a dataset
path <- "https://github.com/rehan13/ownprac/blob/main/testsheet.csv"
out_dir <- tempfile()
dataset <- read_dataset(path, out_dir)


```

Another example is how you can clean data.

```{r}
# Given a dummy data called test_df
test_df <- data.frame(col1 = c(1, 2, 3),
                      col2 = c(4, 5, 6),
                      col3 = c(7, 8, 9))


# Running EDA function for testing
eda_df <- EDA(test_df, select_cols = c("col1", "col2"), col1 > 1, col2 > 5)
eda_df
```

We can also generate plots using the function in this library. But first we will take a test_df here to use for both plots

```{r}
data_test <- data.frame(
  revenue = c(1,2,3),
  budget = c(5,6,7)
)

```

Now we are going to make a scatter plot and correlation plot with this data frame.

```{r}
scatter_plot = plot_scatter_graph(data=data_test,
                                  x_axis_data=revenue,
                                  y_axis_data=budget, x_axis_label="Revenue",
                                  y_axis_label="Budget", title_label = "Scatter Plot", text_size=20)
scatter_plot
```

```{r}
correlation_plot = correlation_plot(data_test, "correlation")
correlation_plot
```

## License

This project, developed by Rehan Mondal and Abheet Kansal, is licensed under the terms of the MIT license.

Permission is hereby granted, free of charge, to any person obtaining a copy of this software and associated documentation files (the "Software"), to deal in the Software without restriction, including without limitation the rights to use, copy, modify, merge, publish, distribute, sublicense and/or sell copies of the Software, and to permit persons to whom the Software is furnished to do so, subject to the following conditions:

The above copyright notice and this permission notice shall be included in all copies or substantial portions of the Software.

THE SOFTWARE IS PROVIDED "AS IS", WITHOUT WARRANTY OF ANY KIND, EXPRESS OR IMPLIED, INCLUDING BUT NOT LIMITED TO THE WARRANTIES OF MERCHANTABILITY, FITNESS FOR A PARTICULAR PURPOSE AND NONINFRINGEMENT. IN NO EVENT SHALL THE AUTHORS OR COPYRIGHT HOLDERS BE LIABLE FOR ANY CLAIM, DAMAGES OR OTHER LIABILITY, WHETHER IN AN ACTION OF CONTRACT, TORT OR OTHERWISE, ARISING FROM, OUT OF OR IN CONNECTION WITH THE SOFTWARE OR THE USE OR OTHER DEALINGS IN THE SOFTWARE.
